Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-02-12 paper/ms.tex
Can you guess which paper?

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_hybrid.png}
\caption{\label{fig:nithybrid}
Estimated \Ni{56} mass vs.\ time for ten hybrid model explosion simulations. 
Shown are realizations 21-30. 
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_CO.png}
\caption{\label{fig:nitco}
Estimated \Ni{56} mass vs.\ time for ten C/O model explosion simulations.
Shown are realizations 21-30. 
}
\end{figure}
The estimated production of \Ni{56} as a function of simulation time
for 10 simulations of explosions from the hybrid progenitor is shown
in Figure \ref{fig:nithybrid} and from the traditional C-O progenitor is
shown in Figure \ref{fig:nitco}.
The figures show that the final Estimated \Ni{56} for the C-O model is
slightly larger then the hybrid model. Therefore, the C-O produces more
\Ni{56}. The hybrid model has a larger range then the C-O model. Also, on
average, the CO model reaches the DDT phase sooner then the hybrid model.

This is a plot of the estimated \Ni{56} yield vs. mass below 2e7 g/cc at
the time of the DDT.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens.pdf}
\caption{\label{fig:masshighdens}
This is a plot of the estimated Ni56 yield vs. mass below 2e7 g/cc at the time of the DDT. 
The degree of expansion was found using the time at which the first detonation point occurred, and the mass at density less then 2e7 g/cc. The estimated Ni56 Yield is the final estimated mass of the model. 
Hybrid- Red
CO- Blue
For a given amount of mass at high density, the CO produces more Iron group elements then the Hybrid model.  
The rectangular regions show one standard deviation from the average for both the C/O and hybrid 
models (SEE DON'S PAPER)
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
\caption{\label{fig:conversion}
The conversion of Ni56 to Iron group elements are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
First is that higher critical density leads to higher electron capture resulting in less Ni56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_hybrid.png}
\caption{\label{fig:nithybrid}
Estimated \Ni{56} mass vs.\ time for ten hybrid model explosion simulations. 
Shown are realizations 21-30. 
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_CO.png}
\caption{\label{fig:nitco}
Estimated \Ni{56} mass vs.\ time for ten C-O model explosion simulations.
Shown are realizations 21-30. 
}
\end{figure}

The estimated production of \Ni{56} as a function of simulation time
for 10 simulations of explosions from the hybrid progenitor is shown
in Figure \ref{fig:nithybrid} and from the traditional C-O progenitor is
shown in Figure \ref{fig:nitco}.
The figures show that the final estimated \Ni{56} for the C-O model is
slightly larger then the hybrid model. Therefore, the C-O produces more
\Ni{56}. The hybrid model has a larger range then the C-O model. Also, on
average, the CO model reaches the DDT phase sooner then the hybrid model.
Both figures show that production of \Ni{56} effectively ceases (the
curves flatten out) well before the end of the simulations at 
$4.0$~\second. Also, the figures show that a few simulations
did not complete. {\color{red} OFFER A WHY?}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens.pdf}
\caption{\label{fig:masshighdens}
Final estimated IGE {\color{red} 
TO BE SURE- NOT \Ni{56} AS FIGURE IS LABELED?} yield 
vs.\ mass {\color{red} above} $2\times 10^7~\grampercc$
at the time of the first DDT in a simulation.  Individual 
realizations are shown (C-O-NE
progenitors in red, C-O in blue) along with rectangles of length
$\pm 1 \sigma$ along each axis and centered at their average values 
for C-O and C-O-Ne.
}
\end{figure}

Figure \ref{fig:masshighdens} compares the final yield of IGE elemets
for the C-O and C-O-Ne simulation suites with the amount of expansion of the
WD during the deflagration phase. The amount of expansion is 
characterized by the mass above $2 \times 10^7~\grampercc$ at the 
time of the DDT, with more high-density mass
indicating less expansion during deflagration. The averages of both
the C-O and C-O-Ne suites along both axes are indicated by the shaded
regions with $\pm1\sigma$ widths.

As expected from previous studies, the trend for both C-O and C-O-Ne
models is that less expansion during the deflagration phase results in
greater IGE yields, because less expansion gives more high
density fuel to be consumed in the detonation.
being more high density fuel for the detonation to consume. 
As the amount of expansion increases (the less
mass above $2 \times 10^7 \grampercc$), 
for a similar amount of expansion, the C-O
models tend to yield greater IGE mass. Following 
\citet{willcoxetal2016}, we interpret
the lower IGE yield in C-O-Ne models as resulting 
from the lower \C{12} abundance and the fact that given
similar fuel density, the \Ne{20}-rich fuel will burn to cooler
temperatures than fuel in the C-O models. The result is
slower burning to IGE and thus a lower IGE yield.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
\caption{\label{fig:conversion}
	The conversion of \Ni{56} to IGEs are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
First is that higher critical density leads to higher electron capture resulting in less Ni56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
}
\end{figure}
Figure \ref{fig:conversion} shows the estimated \Ni{56} yields 
across the range of masses burned to IGE
for all C-O and C-O-Ne realizations at the end 
of the simulaitons ($4.0$~\second),
at which point the total mass burned to \Ni{56} had become constant.
